Fatness of Simple Polygons

### 2018-04-04 proposal/main.tex
Finished proposal

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\abs}[1]{\vert#1\vert}
\DeclareMathOperator*{\argmin}{\textrm{arg\,min}}

@@

[From Professor Mitchell's description.]
Computing the Niceness of a Polygonal Shape. There are various notions of
quantifying how “nice” or how “fat” a simple polygon $P$ is. A “nicest” polygon
might be a regular $n$-gon, which most closely approximates a circular disk. This
project seeks to implement some precise metrics for niceness, and compare them
on simple polygons (possibly moused in by a user or read in from a file, etc).
To make it simple and discrete, I propose that you discretize the boundary of
$P$ with discrete points $p_i$ (additional vertices), with a prescribed spacing,
$\delta$. (That is, for edges of $P$ longer than $\delta$, add vertices along
  the edge so that the new sub-segments are of length at most $\delta$, for a
user-specified parameter $\delta$.)

Then, consider discrete choices of radii $r = \rho, 2\rho, 3\rho, \ldots$ for
disks, $B(p_i,r)$, centered at the discrete boundary points $p_i$, for each
radius $r$. The (discrete) fatness of $P$ is given by the smallest value of the
ratio $\lambda (B(p_i,r)\cap P)/\lambda (B(p_i, r)$, over all choices of $p_i$ and $r =
  \rho, 2\rho, 3\rho, \ldots$ such that $P$ is not contained fully
  inside$B(p_i,r)$.

@@

\begin{definition}
  Let $f : \mathcal{P} \to \RR$. For a given $P \in \mathcal{P}$,
  its \emph{chord-$f$ score} is given by
  \begin{equation*}
    s_f(P) = \min_{x,y \in P} \max(f(P'), f(P''))
  \end{equation*}
  where the chord $[x,y]$ partitions $P = P' \cup P''$.
\end{definition}

@@

%\section{Inferences and Questions}
%The decomposition of the polygon results in some fat Polygons as well as some bad Polygons. We see that a fat Polygon is made a bad Polygon by inserting the bad polygon. This makes me wonder about the union of the Simple Polygons NICE+BAD, BAD+BAD, NICE+NICE. 
%\subsubsection{Questions} 
%\begin{enumerate}
%\item Q1: Given a Simple Polygon, does it fatness depend on the fatness of the
%  individual polygons its made of?
%\item Q2: So, for an individual polygon, without loss of generality lets assume that every Simple Polygon is made up of triangles. So, to measure the fatness of a polygon, we  have to measure the fatness of a triangle. So, the next question we ask ourselves is the fatness of any given triangle, the simplest polygon.
%\item
%Q3: Can we get the fatness of the triangle using the $\alpha$-fatness using the formula given above, whereas is it possible to use squares instead of circles as we know our boundary is a Polygon with straight lines but not a curve.
%Q4: About the defnition of the $\alpha-fatness$
%Q5: Why do we have to discretize the 
%Q6: Alternative measures like, possibly bad unions of nice polygons or visibility kernal ratio. 
%Q7: 
%\end{enumerate}

>>>>

\documentclass[10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\abs}[1]{\vert#1\vert}
\newcommand{\set}[1]{\{#1\}}
\DeclareMathOperator*{\argmin}{\textrm{arg\,min}}

@@

\paragraph{Professor Mitchell's description.}
Computing the Niceness of a Polygonal Shape. There are various notions of
quantifying how “nice” or how “fat” a simple polygon $P$ is. A “nicest” polygon
might be a regular $n$-gon, which most closely approximates a circular disk. This
project seeks to implement some precise metrics for niceness, and compare them
on simple polygons (possibly moused in by a user or read in from a file, etc).
To make it simple and discrete, I propose that you discretize the boundary of
$P$ with discrete points $p_i$ (additional vertices), with a prescribed spacing,
$\delta$. (That is, for edges of $P$ longer than $\delta$, add vertices along
  the edge so that the new sub-segments are of length at most $\delta$, for a
user-specified parameter $\delta$.)

Then, consider discrete choices of radii $r = \rho, 2\rho, 3\rho, \ldots$ for
disks, $B(p_i,r)$, centered at the discrete boundary points $p_i$, for each
radius $r$. The (discrete) fatness of $P$ is given by the smallest value of the
ratio $\lambda (B(p_i,r)\cap P)/\lambda (B(p_i, r))$, over all choices of $p_i$
and $r = \rho, 2\rho, 3\rho, \ldots$ such that $P$ is not contained fully inside
$B(p_i,r)$.

@@

\begin{definition}
  Let $f : \mathcal{P} \to \RR$. For a given $P \in \mathcal{P}$,
  its \emph{chord-$f$ score} is given by
  \begin{equation*}
    s_f(P) = \inf_{x,y \in \partial P} \max(f(P'), f(P''))
  \end{equation*}
  where the chord $[x,y]$ partitions $P = P' \cup P''$.
\end{definition}

@@

Equipped with an $L_p$ norm ($p \in [1,\infty]$), denote by $B(x,\rho)$ the
closed ball of radius $\rho > 0$ centered at $x \in \RR^2$.  The natural choice
is simply the Euclidean norm, but $L_{\infty}$ provides a setting for which
computing $B(x,\rho) \cap P$ resolves to polygonal intersection. By topological
equivalence, we lose no specificity. A final measure of ``fatness'' measures
local nonconvexities of $P$ and identifies the most offending ratio.
\begin{definition}
  The \emph{$\alpha$-fatness score} is given by
  \begin{equation*}
    \alpha(P) = \inf\set{\frac{\lambda(B(x,\rho) \cap
    P)}{\lambda(B(x,\rho))} : x \in \partial P, \rho > 0, P \not\subseteq B(x,\rho)}
  \end{equation*}
\end{definition}

For a given $S \subseteq \RR^2$, let $\mathcal{C}(x,S)$ denote the connected
component of $S$ containing $x$. An alternative formulation of $\alpha$-fatness
replaces $B(x,\rho) \cap P$ with its connected component: $\mathcal{C}(x,
B(x,\rho) \cap P)$. In principle, $\alpha(P)$ is computed by sweeping
continuously, but for simplicity we can merely discretize $\partial P$ with a
parameter $\delta > 0$ indicating the maximal distance between points in
$\partial P$.
